BANTER for Beaked Whales: Hawaii

### 2023-02-07 hawaii/beakerBanter_hawaii.Rmd
Update manuscript and hawaii data
Extensive work on Manuscript and preparation of Hawaii data (in folder). Hawaii data *should* be good to knit. Manuscript has references, needs updated results, figures, inline data, and updated discussion.

---
title: "BANTER for Beaked Whales: Hawaii"
author: "Shannon Rankin"
date: "2022-12-07"
output: html_document
editor_options: 
  markdown: 
    wrap: 72
---

@@

```{r, load packages, message=FALSE}
library(PAMpal)
library(banter)
library(rfPermute)
library(here)
here()
```

Set up our PPS (PAMPal Settings Object) for the Hawaii dataset

@@

4.  Filter out unwanted data: (1) subset and rename species for BANTER
    model and (2) filter to retain only Channel 1.

@@

```{r, identify model}
#model <- banter_model_ici
model <- banter_model
```

@@

```{r, extract RF model}
banter_model_RF <- getBanterModel(model)
```

@@

```{r, confusion matrix, include=TRUE}
hawaii_confuseMatrix <- confusionMatrix(banter_model_RF)
```

@@

```{r, plot votes, include=TRUE}
png("hawaii_votes.png", width = 20, height = 20, units = 'cm',  res = 300)
plotVotes(banter_model_RF)
dev.off()
plotVotes(banter_model_RF)
```

```{r, importance heat map, include=TRUE}
png("hawaii_importance.png", width = 30, height = 25, units = 'cm',  res = 300)
plotImportance(banter_model_RF, plot.type="heatmap")
dev.off()
plotImportance(banter_model_RF, plot.type="heatmap")
```

```{r, proximity plot, include=TRUE}
png("hawaii_proximity.png", width = 20, height = 20, units = 'cm',  res = 300)
hawaii_proximityPlot <- plotProximity(banter_model_RF)
dev.off()
hawaii_proximityPlot <- plotProximity(banter_model_RF)
```

>>>>

---
title: "BANTER for Beaked Whales: Hawaii"
author: "Shannon Rankin"
date: "2022-02-06"
output: html_document
editor_options: 
  markdown: 
    wrap: 72
---

@@

```{r, load packages, message=FALSE}
library(PAMpal)
library(banter)
library(rfPermute)
library(kableExtra)
library(here)
here()
```

1.  Set up our PPS (PAMPal Settings Object) for the Hawaii dataset

@@

3.  Filter out unwanted data: (1) subset and rename species for BANTER
    model and (2) filter to retain only Channel 1.

@@

```{r, identify model}
model <- banter_model
modelname <- "banter_model"

model_ici <- banter_model_ici
modelname_ici <- "banter_model_ici"
```

@@

```{r, extract RF model}
banter_model_RF <- getBanterModel(model)
banter_model_ici_RF <- getBanterModel(model_ici)
```

@@

```{r, confusion matrix, include=TRUE}
hawaii_confuseMatrix <- rfPermute::confusionMatrix(banter_model_RF)
hawaii_confuseMatrix <- kable(hawaii_confuseMatrix, align = "c", digits = c(0,0,0,0,2,2,2))%>%
  kable_classic()%>%
  column_spec(5, border_right = TRUE)%>%
  row_spec(0, bold = TRUE)%>%
  row_spec(5,hline_after = TRUE)%>%
  row_spec(5, bold = TRUE)%>%
  save_kable(paste(modelname, "hawaii_confuseMatrix.png", sep="_"), zoom = 2)

hawaii_ici_confuseMatrix <- rfPermute::confusionMatrix(banter_model_ici_RF)
hawaii_ici_confuseMatrix <- kable(hawaii_ici_confuseMatrix, align = "c", digits = c(0,0,0,0,2,2,2))%>%
  kable_classic()%>%
  column_spec(5, border_right = TRUE)%>%
  row_spec(0, bold = TRUE)%>%
  row_spec(5,hline_after = TRUE)%>%
  row_spec(5, bold = TRUE)%>%
  save_kable(paste(modelname_ici, "hawaii_ici_confuseMatrix.png", sep="_"), zoom = 2)

```

```{r, proximity plot, include=TRUE}
png(paste(modelname, "hawaii_proximity.png", sep="_"), width = 20, height = 20, units = 'cm', res = 300)
hawaii_proximityPlot <- plotProximity(banter_model_RF)
dev.off()
hawaii_proximityPlot <- plotProximity(banter_model_RF)

png(paste(modelname_ici, "hawaii_proximity.png", sep="_"), width = 20, height = 20, units = 'cm', res = 300)
ici_hawaii_proximityPlot <- plotProximity(banter_model_ici_RF)
dev.off()
ici_hawaii_proximityPlot <- plotProximity(banter_model_ici_RF)
```

```{r, importance heat map, include=TRUE}
png(paste(modelname, "hawaii_importance.png", sep="_"), width = 30, height = 25, units = 'cm', res = 300)
plotImportance(banter_model_RF, plot.type="heatmap")
dev.off()
hawaii_importance <- plotImportance(banter_model_RF, plot.type="heatmap")

png(paste(modelname_ici, "hawaii_importance.png", sep="_"), width = 30, height = 25, units = 'cm', res = 300)
plotImportance(banter_model_ici_RF, plot.type="heatmap")
dev.off()
ici_hawaii_importance <- plotImportance(banter_model_ici_RF, plot.type="heatmap")
```

```{r, plot votes, include=TRUE}
png(paste(modelname, "hawaii_votes.png", sep="_"), width = 20, height = 20, units = 'cm',  res = 300)
plotVotes(banter_model_RF)
dev.off()
hawaii_votes <- plotVotes(banter_model_RF)

png(paste(modelname_ici, "hawaii_votes.png", sep="_"), width = 20, height = 20, units = 'cm',  res = 300)
plotVotes(banter_model_ici_RF)
dev.off()
ici_hawaii_votes <- plotVotes(banter_model_ici_RF)
```

@@
